---
title: "Intro to create_linear"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro to create_linear}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(hw3)
```

## Introduction to create_linear function

To use the function 'create_linear' for 1 continuous response and 1 continuous covariate linear regression model with an intercept using mtcars package:

```{r}
# response: mtcars$mpg 
# covariate: mtcars$wt
result1<-create_linear(response=mtcars$mpg, covariates=data.frame(wt=mtcars$wt), df=mtcars, intercept=1)

result1
```
```{r}
intercept1 <- result1$estimates[1]
slope1 <- result1$estimates[2]
plot(mtcars$mpg, mtcars$wt)
abline(a = intercept1, b = slope1, col = "red")
```

## To use the function 'create_linear' for 1 continuous response and 2 continous covariates linear regression model with an intercept using mtcars package:
```{r}
# response: mtcars$mpg 
# covariate: mtcars$wt and mtcars$cyl
result2<-create_linear(response=mtcars$mpg, covariates=data.frame(wt=mtcars$wt, cyl=mtcars$cyl), df=mtcars, intercept=1)

result2
```

## To use the function 'create_linear' for 1  of  continuous response and 3 continuous covariate linear regression model with no intercept using mtcars package:
```{r}
# response: mtcars$mpg
# covariate: mtcars$wt,  mtcars$cyl, mtcars$am
result3<- create_linear(response= (mtcars$mpg), covariates=data.frame(wt=mtcars$wt, cyl=mtcars$cyl, am=mtcars$am), df=mtcars, intercept=0)
result3
```

## Actual Code and Comparison
```{r}
#First Example
example1<- lm(formula = mpg ~ wt, data = mtcars)
ex1<-summary(example1)$coeff
ex1
#Second Example
example2<- lm(formula = mpg ~ wt+cyl, data = mtcars)
ex2<-summary(example2)$coeff
ex2
#Third Example
example3<- lm(formula = mpg ~ 0 + wt+cyl+am, data = mtcars)
ex3<-summary(example3)$coeff
ex3
```

As seen above, the estimates, SE, t-value, p-value from create_linear are very similar to the true lm function. But there are is rounding difference for different estimates.

## Potential Issues
This model cannot handle factors unless it is converted to numerical levels separately and before inputing the covariates into the model. However, it will work on binary covariate as the indication functions are not necessary for binary covariates.

```{r}
#all.equal(result1, example1)

library(bench)
#bench::mark( custom = create_linear(response = mtcars$mpg, covariates = data.frame(wt = mtcars$wt), df = mtcars, intercept = 1),lm_model = lm(formula = mpg ~ wt, data = mtcars),iterations = 100)

```
Our test does not pass the all.equal and bench functions but it may be due to the length of our values. As you can see from the values, the values from the lm and create_linear are almost identical. However, create_linear may lose precision with very small values. 
